\chapter{LIST OF PUBLICATIONS CO-AUTHORED BY W.F. HOLMGREN}
Peer-reviewed publications:
\begin{enumerate}

\item W.F. Holmgren, R. Trubko, I. Hromada, and A.D. Cronin, \emph{``Measurement of a Wavelength of Light for Which the Energy Shift for an Atom Vanishes"} Physical Review Letters {\bf109}, 243004, (2012). 

\item W.F. Holmgren, I. Hromada, C.E. Klauss, and A.D. Cronin, \emph{``Atom beam velocity measurements using phase choppers"} New Journal of Physics 13, 115007 (2011). 

\item V.P.A. Lonij, C.E. Klauss, W.F. Holmgren, and A.D. Cronin, \emph{``Can atom-surface potential measurements test atomic structure models?''}, Journal of Physical Chemistry {\bf115}, 7134 (2011).

 \item V.P.A. Lonij, C.E. Klauss, W.F. Holmgren, and A.D. Cronin, \emph{``Ratio measurements of atom-surface potentials reveal effect of core electrons''}, Physical Review Letters {\bf105}, 233202 (2010).

 \item W.F. Holmgren, M.C. Revelle, V.P.A. Lonij, and A.D. Cronin \emph{``Absolute and ratio measurements of the polarizability of Na, K, and Rb with an atom interferometer''}, Physical Review A {\bf81}, 053607 (2010).

\item	V.P.A. Lonij, W.F. Holmgren, and A.D. Cronin, \emph{``Magic ratio of window width to grating period for van der Waals potential measurements using material gratings''}, Physical Review A {\bf80}, 062904 (2009).

%\item ??? I. Hromada, W.F. Holmgren, R. Trubko, and A.D. Cronin, \emph{``A lens for atom-waves in an interferometer"}, to be submitted to Physical Review A (2013).

%\item ?????? I. Hromada, W.F. Holmgren, R. Trubko, and A.D. Cronin, \emph{``Absolute and ratio measurements of the polarizability of Na, K, Rb, and Cs''}, to be submitted to Physical Review A (2013).

%\item ?????? R. Trubko, W.F. Holmgren, I. Hromada, and A.D. Cronin, \emph{``Magic-zero wavelength measurements of K"}, to be submitted to Physical Review A (2013).
 
\end{enumerate}



\noindent Presentations and posters:

\begin{enumerate}

\item Chemical Physics Program Seminar, UA Chemistry Dept., 2012, Talk: \emph{``Magic-zero wavelengths and their applications"} W.F. Holmgren, R. Trubko, I. Hromada, and A.D. Cronin.

\item APS DAMOP 2012, Anaheim, Talk: \emph{``Measurement of the first tune-out wavelength of K with an atom interferometer"} W.F. Holmgren, R. Trubko, I. Hromada, and A.D. Cronin.

\item APS DAMOP 2011, Atlanta, Talk: \emph{``Polarizability measurements of the ground and metastable states of Sr, Yb, and Ba"} W.F. Holmgren, I. Hromada, C.E. Klauss, V.P.A Lonij, and A.D. Cronin.

\item APS DAMOP 2010, Houston, Talk: \emph{``Absolute and ratio measurements of the polarizability of Na, K, and Rb"} W.F. Holmgren, M.C. Revelle, V.P.A. Lonij, and A.D. Cronin.

\item APS DAMOP 2010, Houston Poster: \emph{``A multispecies atom interferometer"} I. Hromada, C.E. Klauss, W.F. Holmgren, V.P.A. Lonij, and A.D. Cronin.

\item Low Energy Seminar, UA Physics Dept., 2010, Talk: \emph{``Absolute and ratio measurements of the polarizability of Na, K, and Rb"} W.F. Holmgren, M.C. Revelle, V.P.A. Lonij, and A.D. Cronin.

\item Frontiers of Matterwave Optics 2010, Crete, Greece, Poster: \emph{``Absolute and ratio measurements of the polarizability of Na, K, and Rb"} W.F. Holmgren, M.C. Revelle, V.P.A. Lonij, and A.D. Cronin.

\item APS DAMOP 2009, Charlottesville, Poster: \emph{``Atom interferometry measurements of the polarizability of Na, K, and Rb"}, W.F. Holmgren, M. C. Revelle, V. P. A. Lonij, and A. D. Cronin.

\item APS DAMOP 2007, Poster: \emph{Portable Atom Chip Vacuum Cell for Rapid BEC Production} , M. B. Squires, E. A. Salim, W.F. Holmgren, D. Z. Anderson, S. E. McBride, S. A. Lipp, J. F. Denatale, R. E. Mihailovich.

\end{enumerate}


\noindent Other works:

\begin{enumerate}

\item A.D. Cronin and W.F. Holmgren, \emph{``Matter waves in a new light"} Nature Physics {\bf{9}}, 137, (2013). 

\item A.D. Cronin, W.F. Holmgren, I. Hromada, C.E. Klauss, V.P.A. Lonij, B.J. McMorran, \emph{``New applications for nanogratings in matter wave optics"} Appendix H in V.P.A. Lonij's thesis, available at www.atomwave.org

\item S.E. McBride, S.A. Lipp, J.J. Michalchuk, D.Z. Anderson, W.F. Holmgren, M.B. Squires, \emph{Alkali metal dispenser and uses for same}, U.S. Patent No. 7955551.

\end{enumerate}



